---
title: "Qhite Wine Quality Prediction"
date: "April 20, 2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
---



```{r}
wine_white <- read.csv("/Users/hhuang/Desktop/2019 spring/632/project/wineQualityWhites.csv", header = TRUE)
head(wine_white)
dim(wine_white)
str(wine_white)
```


```{r}
sapply(wine_white, function(x) sum(is.na(x)))
```


```{r}
wine_white <- wine_white[,-1]
wine_white$quality <- as.numeric(wine_white$quality)
head(wine_white)
hist(wine_white$quality)
summary(wine_white)
```

```{r}
pairs(quality ~ ., data = wine_white)
```


```{r}
library(leaps)
regsub_fit <- regsubsets(quality ~ ., data = wine_white, nvmax=11)
regsub_summ <- summary(regsub_fit)

attributes(regsub_summ)

round(regsub_summ$rsq, 4)

round(regsub_summ$adjr2, 4)

which.max(regsub_summ$adjr2)

coef(regsub_fit, 8)
```

```{r}
n <- nrow(wine_white)
aic_vec <- n*log(regsub_summ$rss/n) + 2*c(1:11)

par(mfrow=c(1,3), mar=c(4.5, 4.5, 1, 1))
plot(c(1:11), regsub_summ$adjr2, xlab="Number of Variables", ylab="Adjusted RSqr")
abline(v=which.max(regsub_summ$adjr2))

plot(c(1:11), aic_vec, xlab="Number of Variables", ylab="AIC")
abline(v=which.min(aic_vec))

plot(c(1:11), regsub_summ$bic, xlab="Number of Variables", ylab="BIC")
abline(v=which.min(regsub_summ$bic))
```


```{r}
which.min(aic_vec)
coef(regsub_fit, 8)

which.min(regsub_summ$bic)
coef(regsub_fit, 8)
```


```{r}
wine_full <- lm(quality ~ ., data = wine_white)
wine_sw <- step(wine_full)
summary(wine_sw)
```

```{r}
lm_wine1 <- lm(quality ~ fixed.acidity + volatile.acidity + residual.sugar + free.sulfur.dioxide + density + pH + sulphates + alcohol, data = wine_white)
```

We can write the model lm_loan1 as $CCAvg = \beta_0 + \beta_1 Age + \beta_2 Experience+ \beta_3 Income +  \beta_4 Family + \beta_5 Education + \beta_6 Mortgage + \beta_7 Personal.Loan + \beta_8 CD.Account + \beta_9 Online +e$

```{r}
library(tidyverse)
library(ggplot2)
library(GGally)
wine_white %>% 
  select(quality, fixed.acidity, volatile.acidity, residual.sugar, free.sulfur.dioxide, density, pH, sulphates, alcohol) %>% 
  ggpairs()
```

```{r}
wine_null <- lm(quality ~ 1, data = wine_white)
anova(wine_null ,lm_wine1)
```

Since the p-value < 0.001, we reject the null hypothesis that$\beta_1 = \cdots = \beta_9 = 0$. Thus, we conclude, that at least one predictor is associated with the average spending on credit cards per month ($000).

```{r}
summary(lm_wine1)
```

```{r}
plot(lm_wine1, which = 2)
```

Not noraml.

```{r}
plot(lm_wine1, which = 1)
```

No linear and no constant variance.

Therefore, we need transformation.


```{r}
library(car)
summary(powerTransform(cbind(fixed.acidity, volatile.acidity, residual.sugar, free.sulfur.dioxide, density, pH, sulphates, alcohol) ~ 1, wine_white))
```

```{r}
lm_wine2 <- lm(quality ~ log(fixed.acidity) + log(volatile.acidity) + sqrt(residual.sugar) + sqrt(free.sulfur.dioxide) + density + 1/sqrt(pH) + log(sulphates) + sqrt(alcohol), data = wine_white)
```

```{r}
pairs(quality ~ log(fixed.acidity) + log(volatile.acidity) + sqrt(residual.sugar) + sqrt(free.sulfur.dioxide) + density + 1/sqrt(pH) + log(sulphates) + sqrt(alcohol), data = wine_white)
```

```{r}
plot(lm_wine2, which = 1)
```

```{r}
plot(lm_wine2, which = 2)
```

```{r}
boxCox(lm_wine2)
summary(powerTransform(lm_wine2))
```

```{r}
lm_wine3 <- lm(quality^0.76 ~ log(fixed.acidity) + log(volatile.acidity) + sqrt(residual.sugar) + sqrt(free.sulfur.dioxide) + density + 1/sqrt(pH) + log(sulphates) + sqrt(alcohol), data = wine_white)

summary(lm_wine3)
```

```{r}
par(mfrow=c(1,3), mar=c(4.5, 4.5, 2, 2))
plot(lm_wine3, c(1:2))
plot(predict(lm_wine3), (wine_white$quality)^0.76, xlab="Fitted Values", ylab="log(quality)")
lines(lowess(predict(lm_wine3), (wine_white$quality)^0.76), col='red')
abline(0,1)
```

```{r}
plot(predict(lm_wine1), wine_white$quality, xlab="Fitted Values", ylab="log(quality)")
lines(lowess(predict(lm_wine1), wine_white$quality), col='red')
abline(0,1)
```

```{r}
plot(lm_wine3,which = 5)
```

```{r}
p <- 8 
n <- nrow(wine_white) 
plot(hatvalues(lm_wine3), rstandard(lm_wine3), xlab= 'Leverage' , ylab= 'Standardized Residuals') 
abline(h = c(-4,4),v = 2*(p+1)/n, lty=2)
```

####K-Fold Cross-Validation

```{r}
str(wine_white)
x <- model.matrix(quality ~ ., data=wine_white)[, -12]
y <- wine_white$quality
n <- nrow(x)

compute_mse <- function(y, y_pred) {
  n <- length(y)
  (1 / n) * sum((y - y_pred)^2)
}
```

```{r}
library(caret)
set.seed(999)
(folds <- createFolds(y, k=10))
```

```{r}
mse_vec <- rep(0, 10)
n_vec <- rep(0, 10)
for(k in 1:10) {
  test <- folds[[k]]
  y_test <- y[test]
  y_train <- y[-test]
  x_test <- as.data.frame(x[test, ])
  x_train <- as.data.frame(x[-test, ])
  lm_fit <- lm(y_train ~ ., data = x_train)
  lm_pred <- predict(lm_fit, newdata = x_test)
  mse_vec[k] <- compute_mse(y_test, lm_pred)
  n_vec[k] <- length(folds[[k]])
}

sqrt((1 / n) * sum(n_vec * mse_vec))
```

```{r}
train_idx <- sample(n, size = floor(0.7 * n))

x_train <- x[train_idx, ]
nrow(x_train)

x_test <- x[-train_idx, ]
nrow(x_test)

y_train <- y[train_idx]

y_test <- y[-train_idx]
```

```{r}
lm_wine4 <- lm(quality^0.76 ~ log(fixed.acidity) + log(volatile.acidity) + sqrt(residual.sugar) + sqrt(free.sulfur.dioxide) + density + 1/sqrt(pH) + log(sulphates) + sqrt(alcohol), data = wine_white, subset = train_idx)

compute_rmse <- function(y, y_pred) {
  n <- length(y)
  sqrt((1 / n) * sum((y - y_pred)^2))
}

wine_pred <- predict(lm_wine4, newdata = wine_white[-train_idx, ])
rmse_full <- compute_rmse(y_test, wine_pred)
rmse_full
```

